\documentclass[a4paper,10pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{fontawesome} 
\usepackage{lmodern}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\definecolor{headerblue}{RGB}{0, 102, 204}
\definecolor{sectiongray}{RGB}{64, 64, 64}

\begin{document}
\begin{center}
    {\Huge \textbf{\color{headerblue} PRODYUMNA BOGOHAIN}} \\
    \vspace{1mm}
    \textbf{Postgraduate Student} \\
    \vspace{1mm}
    \small
    \faEnvelope \, \texttt{prodyumnaborgohain@gmail.com} \quad
    \faPhone \, +91-7576871043 \quad
    \faLinkedinSquare \, \texttt{linkedin.com/in/prodyumna-borgohain} \\
\end{center}

\noindent\rule{\textwidth}{0.5pt}
\section*{\color{sectiongray} Education}
\noindent
\textbf{Dibrugarh University} \hfill August 2024 -- Present \\
Postgraduate Degree in\emph{ Computer Applications} \\

\noindent
\textbf{Jorhat Institute of Science and Technology (Assam Science and Technology University)} \hfill September 2021 -- July 2024 \\
Bachelor’s Degree in\emph{ Computer Science and Information Technology} \\
\textbf{CGPA: 8.0}

\noindent\rule{\textwidth}{0.5pt} 
\section*{\color{sectiongray} Skills}
\begin{itemize}[noitemsep]
    \item \textbf{Programming Languages:} C, C++, Java, GitHub, HTML, CSS.
    \item \textbf{Technologies:} Git, LaTeX, Canva, Bootstrap, XAMPP, Blender, Da Vinci, ChatGPT, MS Office, Adobe Suite.
    \item \textbf{Additional Skills:} Public Speaking, Team Collaboration, Problem-solving, Design, Strategy, Analytical.
\end{itemize}

\noindent\rule{\textwidth}{0.5pt} 
\section*{\color{sectiongray} Projects}
\textbf{Graduation Minor Project: Admin-Approved Food Ordering System} \hfill December 2023 
\begin{itemize}[noitemsep]
     \item Developed a streamlined Food Ordering System where customer orders are sent to an admin for approval based on availability.
     \item \textbf{Tools Used:} HTML, CSS, PHP, XAMPP.
\end{itemize}
\textbf{Graduation Major Project: Tea Inventory and Sales Management System} \hfill July 2024 
\begin{itemize}[noitemsep]
     \item Developed a Tea Factory Management System (TFMS) to streamline sales, purchases, and inventory management, featuring a graphical dashboard for a comprehensive view of key metrics.
     \item \textbf{Tools Used:} HTML, CSS, Bootstrap, PHP, XAMPP.
\end{itemize}
\textbf{Website for a Resort: De Heelios} \hfill February 2024 
\begin{itemize}[noitemsep]
     \item Developed a static website for a resort near Manas Wildlife Sanctuary to establish an online presence and provide easy contact.
     \item \textbf{Tools Used:} WordPress, Hostinger, Canva, After Effects, Photoshop.
\end{itemize}

\noindent\rule{\textwidth}{0.5pt} 
\section*{\color{sectiongray} Extracurricular Activities}
\begin{itemize}[noitemsep]
    \item Formed and led a Dance Club/Society at college; organized and participated in several events.
    \item Co-composed the anthem of VED Academy.
    \item Organized various events under the university’s techno fest.
    \item Active member of NSS with 3 years of experience.
\end{itemize}

\noindent\rule{\textwidth}{0.5pt} 

\end{document}
